Rethinking sampling functions to include weights and numbers

### 2019-05-10 RethinkSamplingFunctions.Rmd
fix typo

1. apply `run_truth` to a set of Atlantis model outputs, which returns 'atoutput' components in the following units by species, agecl (Atlantis cohort, often in units of maxage/10), polygon (model box), layer (model depth), and time (model toutinc or outputstep):
    + `biomass_eaten$atoutput` is eaten biomass in t for each functional group?
        + `biomass_eaten$vol` is volume aggregated over layers
        + `biomass_eaten$prey` is the prey item eaten?
        + `biomass_eaten$dietcomp` is proportion in diet?
        + `biomass_eaten$bio_eaten` is different from atoutput but how?
    + `biomass_ages$atoutput` is  biomass in t from `calc_biomass_age`
    + `catch$atoutput` is fishery catch in numbers of individuals
    + `nums$atoutput` is numbers of individuals
    + `resn$atoutput` is Nitrogen reserve weight in mg/m^3
    + `structn$atoutput`is Nitrogen reserve weight in mg/m^3
2. additional components of the `run_truth` return (default name `result`) are key factors needed for conversions and interpreting the outputs (described elsewhere):
    + `biolprm`
    + `fgs`
3. apply `create_survey` to the result output of `run_truth`
4. apply `sample_survey_biomass` to the output of `create_survey` to get an index
    + designed to use nums output with an average weight--but estimating average weight proved problematic the way I did it, which was too imprecise
    + can be used directly on biomass_ages output with a vector of average weight=1 (see [True Bio Test](https://sgaichas.github.io/poseidon-dev/TrueBioTest.html))
5. apply `sample_fish` to the output of `create_survey` to generate biological samples
6. apply `calc_age2length` to output of 'sample_fish` to generate length compositions
    + *FIRST BIG PROBLEM!* `calc_age2length` needs weight data at the same level of resolution as the nums data to estimate lengths using the length-weight relationship. 
    + Weight data comes from resn and structn. `calc_age2length` was originally tested with completely disaggregated outputs of `run_truth` and it generates length samples correctly that way
    + Initial `calc_age2length` testing with a real dataset revealed that it is entirely too slow to apply at the level of `run_truth` results for a full Atlantis model run and over many species (TrueLengthCompTest.Rmd)
    + Attempts to aggregate structn and resn results to the `create_survey` and `sample_fish` level were incorrect, because:
    + *we cannot apply functions designed for numbers output that aggregate based on sum to resn and structn outputs which are in units of N per volume*
    + So actually, this problem reaches all the way back to `create_survey` which is designed for nums output and aggregates using a sum:

>>>>

1. apply `run_truth` to a set of Atlantis model outputs, which returns 'atoutput' components in the following units by species, agecl (Atlantis cohort, often in units of maxage/10), polygon (model box), layer (model depth), and time (model toutinc or outputstep):
    + `biomass_eaten$atoutput` is eaten biomass in t for each functional group?
        + `biomass_eaten$vol` is volume aggregated over layers
        + `biomass_eaten$prey` is the prey item eaten?
        + `biomass_eaten$dietcomp` is proportion in diet?
        + `biomass_eaten$bio_eaten` is different from atoutput but how?
    + `biomass_ages$atoutput` is  biomass in t from `calc_biomass_age`
    + `catch$atoutput` is fishery catch in numbers of individuals
    + `nums$atoutput` is numbers of individuals
    + `resn$atoutput` is Nitrogen reserve weight in mg/m^3
    + `structn$atoutput`is Nitrogen reserve weight in mg/m^3
2. additional components of the `run_truth` return (default name `result`) are key factors needed for conversions and interpreting the outputs (described elsewhere):
    + `biolprm`
    + `fgs`
3. apply `create_survey` to the result output of `run_truth`
4. apply `sample_survey_biomass` to the output of `create_survey` to get an index
    + designed to use nums output with an average weight--but estimating average weight proved problematic the way I did it, which was too imprecise
    + can be used directly on biomass_ages output with a vector of average weight=1 (see [True Bio Test](https://sgaichas.github.io/poseidon-dev/TrueBioTest.html))
5. apply `sample_fish` to the output of `create_survey` to generate biological samples
6. apply `calc_age2length` to output of `sample_fish` to generate length compositions
    + *FIRST BIG PROBLEM!* `calc_age2length` needs weight data at the same level of resolution as the nums data to estimate lengths using the length-weight relationship. 
    + Weight data comes from resn and structn. `calc_age2length` was originally tested with completely disaggregated outputs of `run_truth` and it generates length samples correctly that way
    + Initial `calc_age2length` testing with a real dataset revealed that it is entirely too slow to apply at the level of `run_truth` results for a full Atlantis model run and over many species (TrueLengthCompTest.Rmd)
    + Attempts to aggregate structn and resn results to the `create_survey` and `sample_fish` level were incorrect, because:
    + *we cannot apply functions designed for numbers output that aggregate based on sum to resn and structn outputs which are in units of N per volume*
    + So actually, this problem reaches all the way back to `create_survey` which is designed for nums output and aggregates using a sum:
